\section{Glossary:}
\vspace{0.2in}

\begin{itemize}
\item \textbf{Activity diagram} - A UML diagram that depicts the flow of actions or activities in the process.
\item \textbf{API} - Application Programming Interface
\item \textbf{Application} -Both renewal applications or new fellowship applications are seen as applications by this project.
\item \textbf{CV} - Curriculum Vita
\item \textbf{Domain objects} - Are the objects that are present in the system being modelled.
\item \textbf{EAI} - Enterprise Application Integration
\item \textbf{NRF} - National Research Foundation
\item \textbf{Spreadsheet} - A special type of computer document that is used to represent data in rows and columns.
\item \textbf{GlassFish} - GlassFish is a web server software package that is very flexible and compatible with Java EE applications. 
\item \textbf{HTML} - Hyper Text Mark-up Language
\item \textbf{HTML Scrpping} -  technique of extracting information from websites
\item \textbf{HTTPS} - Hyper Text Transfer Protocol Secure is a higher level network oriented communication rule set that is highly secure and is used by all web browsers. 
\item \textbf{Java EE} - Java Enterprise Edition
\item \textbf{MySQL} - Is a relational persistence database package that provides all the necessary management tools to run and manage a database server.
\item \textbf{Object-Oriented} - A programming language style that encapsulates everything as an object instance of a particular class of attributes and methods.
\item \textbf{JDBC} - Java Database Connection
\item \textbf{MVC} - Model View Controller
\item \textbf{PDF} - Portable Document Format file
\item \textbf{Peoplesoft} - A management system designed by oracle. 
\item \textbf{Spreadsheet} - A special type of digital document that is used to represent data in rows and columns
\item \textbf{UI} - User Interface
\item \textbf{Use case diagram} - A UML diagram that gives a visual depiction of a service or group of services.
\item \textbf{UML} - Unified modelling language. A commonly used model standard to provide technology neutral models of different aspects of software.
\item \textbf{UP} - University of Pretoria
\item \textbf{Work Flow} - Describes the tasks, procedural steps and tools needed for each step in a business process
\end{itemize}		


\vspace{0.5in}
